Analyzing Fairness: Race, Recidivism, and the COMPAS Algorithm

### 2022-04-19 final_metrics_analysis.Rmd

```{python post-processing equal odds needs fix} 
#ep = EqOddsPostprocessing(unprivileged_groups=0, privileged_groups= 1, seed =1234567)
#eo = PostProcessingMeta(estimator=lr, postprocessor=ep, random_state=1234567)
#eo.fit(train_BLD, test_BLD)
#y_pred_EO = eo.predict(test_BLD)
#y_proba_EO = eo.predict_(test_BLD)
```

>>>>

```{python}
def get_attributes(data, selected_attr=None):
    unprivileged_groups = []
    privileged_groups = []
    if selected_attr == None:
        selected_attr = data.protected_attribute_names

    for attr in selected_attr:
            idx = data.protected_attribute_names.index(attr)
            privileged_groups.append({attr:data.privileged_protected_attributes[idx]}) 
            unprivileged_groups.append({attr:data.unprivileged_protected_attributes[idx]})

    return privileged_groups, unprivileged_groups
```

```{python post-processing equal odds needs fix} 
privileged_groups, unprivileged_groups = get_attributes(train_BLD, selected_attr= 'race')
ep = EqOddsPostprocessing(unprivileged_groups= unprivileged_groups, privileged_groups= privileged_groups, seed = 42)
#eo = PostProcessingMeta(estimator=lr, postprocessor=ep, random_state=1234567)
EOPP = ep.fit(train_BLD, test_BLD)
y_pred_EO = ep.predict(test_BLD)
#y_proba_EO = ep.predict_(test_BLD)

acc_EO = accuracy_score(y_test, y_pred_EO)
```
